### 2021-12-03 paper/abstract.tex
abstract

\noindent \textbf{CAKE: Computational and Automated Kantian Ethics}

@@

\noindent \textbf{Abstract}: As artifically intelligent agents become increasingly powerful, the need for philosophically
sophisticated automated ethical reasoning becomes more pressing. Representing a robust ethical theory 
to a computer poses technical and ethical challenges. I argue that, out of the three major ethical traditions, Kantian ethics is
most natural to formalize because it presents inviolable, context-agnostic, formal rules. In this paper, 
I present CAKE, an implementation of automated Kantian ethics that is faithful to the rich Kantian 
philosophical tradition. I formalize Kant's categorical imperative in deontic logic, implement this 
formalization in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
my implementation coheres with expected properties of Kantian ethics. Not only is CAKE an early step 
towards philosophically rich ethical AI agents, it also establishes that computational tools can help 
philosophers reach ethical insights.

>>>>

\noindent \textbf{FAKE: Faithful Automated Kantian Ethics}

@@

\noindent \textbf{Abstract}: Calls from regulators, philosophers, and computer scientists for the ethical
use and development of artifical intelligence have spurred interest in automated ethics. Such machine 
ethics will best cohere with intuitions and guide action when it is faithful to existing philosophical
literature. Automating philosophically sophisticated ethical theories poses technical and philosophical
challenges because it requires translating
complex ethical theories expressed in natural language to the rigid syntax of a computer program. In 
this paper, I present FAKE: an implementation of automated Kantian 
ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical 
traditions, Kant's categorical imperative is most natural to formalize because it presents inviolable, 
context-agnostic, formal rules.  I formalize Kant's categorical imperative 
in Carmo and Jones's dyadic deontic logic, implement this formalization 
in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
different formalizations cohere with expected properties of Kantian ethics, as established in the literature. 
FAKE is not only an early step towards philosophically mature ethical AI agents, but it can also help
philosophers reach new ethical insights, thus paving the way for computational ethics.
